Czech parliament meeting recordings as ASR training data

### 2020-06-24 2020-fedcsis-sofia-svolocz/svolocz.tex
add fedcsis svolocz paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Czech parliament meeting recordings as ASR training data}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Jan Oldřich Krůza\inst{1}\orcidID{0000-0002-7510-6470}}
%
\authorrunning{Jan Krůza}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
\email{kruza@ufal.mff.cuni.cz}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these data.
\keywords{speech corpus, speech recognition, czech}
\end{abstract}

@@

\begin{figure}[htpb]
\includegraphics[scale=0.25]{rc/overlap.eps}
\caption{Alignment and overlap of audio files and transcript. The examples are
from Feb. 12th 2020 around 10 o'clock. The transcript corresponding to the
recording in the upper left covers audio positions 01:34 - 11:24. The one in the
lower right from 01:24 to 12:00.}
\label{fig:overlap}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[scale=0.4]{rc/align.eps}
\caption{Schema of aligning the audio to the stenographic transcript on word
level.}
\label{fig:align}
\end{figure}

@@

@@

Apart from them, I used the publicly not available corpora of Charles University
Corpus of Financial News (CUCFN, 65 hours)\cite{byrne1999large}, the Balanced
corpus of informal spoken Czech (Oral2013, 293 hours)\cite{oral2013} and the
spoken Bible (100 hours) available with no license terms from {\em
poslouchamebibli.cz}. Table~\ref{tab:csasr:results} shows the speech recognition
results for each corpus on test data from itself and on a common test set from
all the corpora.

\begin{table}[htpb]
\begin{center}
\begin{tabular}{|l||r|r|}
\hline
source    & WER on self & WER on all \\
\hline
bible     & 9.20\%  & 94.7\% \\
cucfn     & 31.6\%  & 72.8\% \\
makon     & 30.4\%  & 77.3\% \\
oral2013  & 78.4\%  & 60.7\% \\
ovm       & 21.6\%  & 72.9\% \\
\textbf{parliament}
          & 8.74\%  & \textbf{39.7\%} \\
vystadial & 51.0\%  & 74.0\% \\
\hline
all       & 28.4\%  & 28.4\% \\
\hline
\end{tabular}
\caption{Word error rate of speech recognition on the individual corpora and on
their concatenation.}\label{tab:csasr:results}
\end{center}
\end{table}

@@

Source code for scraping and building the corpus is in the public domain and
available on \texttt{GitHub.com/Sixtease/cz-parliament-speech-corpus}.

@@

\bibliographystyle{splncs}

\bibliography{citace}

>>>>

% This file demonstrates how to use the IEEEConf LaTeX2e macro package,
% to prepare a manuscript for proceedings on CD of the conference
% FedCSIS
%
\documentclass[conference]{IEEEtran}
%\documentclass[a4paper]{IEEEconf}

% This package serves to balance the column lengths on the last page of the document.
% please, insert \balance command in the left column of the last page
\usepackage{balance}

%% to enable \thank command
\IEEEoverridecommandlockouts 
%% The usage of the following packages is recommended
%% to insert graphics
\usepackage[dvips]{graphicx}
% to typeset algorithms
% to typeset code fragments
\usepackage{listings}
% provides various features to facilitate writing math formulas and to improve the typographical quality of their output.
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
% por urls typesetting and breaking
\usepackage{url}
% for vertical merging table cells
\usepackage{multirow}

% define environments for remarks and examples
\newtheorem{remark}{Remark}[section]
\newtheorem{example}[remark]{Example}

%
%
\title{Czech parliament meeting recordings as ASR training data}
%
%
\author{
\IEEEauthorblockN{Jan Oldřich Krůza}
\IEEEauthorblockA{
Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University\\
Email: kruza@ufal.mff.cuni.cz}
}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

\begin{document}
\maketitle              % typeset the title of the contribution

\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these and other data.
\end{abstract}

@@

\begin{figure*}[tpb]
\centering
\includegraphics[width=0.9\hsize]{rc/overlap.eps}
\caption{Alignment and overlap of audio files and transcript. The examples are
from Feb. 12th 2020 around 10 o'clock. The transcript corresponding to the
recording in the upper left covers audio positions 01:34 - 11:24. The one in the
lower right from 01:24 to 12:00.}
\label{fig:overlap}
\end{figure*}

@@

\begin{figure*}[htpb]
\includegraphics[width=0.9\hsize]{rc/align.eps}
\caption{Schema of aligning the audio to the stenographic transcript on word
level.}
\label{fig:align}
\end{figure*}

@@

\section{Numerals and Abbreviations}

@@

Apart from them, I used the publicly not available corpora of Charles University
Corpus of Financial News (CUCFN, 65 hours)\cite{byrne1999large}, the Balanced
corpus of informal spoken Czech (Oral2013, 293 hours)\cite{oral2013} and the
spoken Bible (100 hours) available with no license terms from
\url{poslouchamebibli.cz}. Table~\ref{tab:csasr:results} shows the speech recognition
results for each corpus on test data from itself and on a common test set from
all the corpora.

\begin{table}[htpb]
\caption{Word error rate of speech recognition on the individual corpora and on
their concatenation.}
\centering
\begin{tabular}{|l||r|r|}
\hline
source    & WER on self & WER on all \\
\hline
bible     & 9.20\%  & 94.7\% \\
cucfn     & 31.6\%  & 72.8\% \\
makon     & 30.4\%  & 77.3\% \\
oral2013  & 78.4\%  & 60.7\% \\
ovm       & 21.6\%  & 72.9\% \\
\textbf{parliament}
          & 8.74\%  & \textbf{39.7\%} \\
vystadial & 51.0\%  & 74.0\% \\
\hline
all       & 28.4\%  & 28.4\% \\
\hline
\end{tabular}
\label{tab:csasr:results}
\end{table}

@@

Source code for scraping and building the corpus is in the public domain and
available on 
\url{GitHub.com/Sixtease/cz-parliament-speech-corpus}.

@@

\bibliographystyle{myIEEEtran}
\bibliography{citace}
